Implementation of an Open-Source modular mangetic field camera hardware for usage in Low-Field MRI Systems

### 2023-10-11 documentation/paper/main.tex
.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[ngerman]{babel}
\usepackage[acronym]{glossaries}
\usepackage{url}
%\usepackage{setspace}
\makeglossaries
\newacronym{mri}{MRI}{Serious Games}

@@

\title{Implementation of an Open-Source modular mangetic field camera for usage in Low-Field MRI Systems}

@@

\begin{IEEEkeywords}
%Serious Gaming (\gls{sg}), \gls{vr}, Extended Reality (\gls{xr}), Computer Grafik (\gls{cg})
\end{IEEEkeywords}

@@

\subsection{Sensor selection}
%tabelle möglicherdigitaler sensoren
% mixture of sensors
% tablee with ranges
% digital only at the moment
\subsection{Sensor slice}

@@

@@

\subsection{Powermanagement}
sensor on off

\subsection{Sensor-Selection}
%tabelle möglicherdigitaler sensoren

@@

% 3d printed cases for magnet holders
%
%-----------------------------------------------------------------------------------------------------------------------------------------------
% Embedded System Software
\section{Embedded System Software}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[ngerman]{babel}
\usepackage[acronym]{glossaries}
\usepackage{url}
%\usepackage{setspace}
\makeglossaries
\newacronym{mri}{MRI}{Magnetic resonance imaging}

@@

\title{Implementation of an Open-Source modular mangetic field camera hardware for usage in Low-Field MRI Systems}

@@

\begin{IEEEkeywords}
magnetic resonance imaging (\gls{mri})
\end{IEEEkeywords}

@@

\subsection{Sensor selection}

\begin{table}
    \centering
    \begin{tabular}{|l|c|}
    \hline
    \textbf{Name} & \textbf{Range (mT)} \\
    \hline
    Honeywell HMC5883L & 1.3 - 8.1 mT \\
    STMicroelectronics LIS3MDL & 4 - 16 mT \\
    TDK InvenSense ICM-20948 & 49 mT \\
    \hline
    \end{tabular}
    \caption{Implemented 3D Magnetometer ICs}
\end{table}

% mixture of sensors
% tablee with ranges
% digital only at the moment
\subsection{Sensor slice}

@@

The sensor slice shown in Figure \ref{anpmagcam_sensor_module_fig_fig} consists of 8 TLV493d sensors spaced 8mm apart on an 8mm x 64mm PCB.
To build a larger sensor array, the golf finger pads of the board can be soldered to other similar boards in a daisy chain configuration.

The daisy chain design simplifies connectivity as multiple slices can be connected in a linear fashion, reducing complex wiring.
This approach simplifies expansion and troubleshooting, as new slices can be easily added or removed without disrupting the entire system.

In this way, an 8x8 sensor array can be built quickly, and the mechanical stability and alignment is ensured by the interconnection of the golf finger pads.

@@

\subsection{Powermanagement}

Each sensor slice also implements its own power management of the sensors, both at the hardware and software level, but this is optional.

Depending on the type of sensor used, the current flowing through the individual layers can influence its measurement result.
Therefore, the control logic and voltage converter components were placed separately from the sensors in the board layout.
In addition, individual sensors can be specifically supplied with voltage. This was implemented using a switchable power supply (PCF847). 
The software is later (when activated) able to activate only the sensor that is to be read out at the current time.
A disadvantage of this implementation, however, is that each sensor must be reconfigured after activating the power supply.
Depending on the selected sensor, this can take up to an additional 10ms per sensor measurement.

@@

% 3d printed cases for magnet holders
%

%-----------------------------------------------------------------------------------------------------------------------------------------------
% Embedded System Software
\section{Embedded System Software}
